\begin{center}
	{\huge{\textbf{Acknowledgement}}}
\end{center}

I am indebted in the preparation of this thesis to my supervisor, Prof. Sanjeev K. Aggarwal of Indian Institute of Technology Kanpur, whose motivation, patience, immense knowledge and enthusiasm have been a source of illumination and inspiration for me. His guidance helped me all the time of research, and evaluating the progress of this work. I could not have imagined a better advisor and mentor, who have granted me so much time to explore the width and depth of this field. When I was wrong, things were not going as expected, he guided me with patience and encouragement. I am glad that I got a chance to work under such a friendly, hard-working and understanding person. I would like to thank Dr. Aggarwal for being a constant source of motivation without which nothing would have been possible.

I would also like to express my sincere gratitude to Dr. Arnab Bhattacharya for his benevolence and support to pursue a research project under him, which helped me to enrich my knowledge in the field of indexing in databases. I would like to thank my instructors Prof. Baswana, Prof. Manindra Agrawal, Prof. Saxena, Prof. Karnick, Prof. Chaudhuri and Prof. T V Prabhakar for teaching me important courses in Masters degree.

I am thankful to Tejas Gandhi for helping me out whenever I am in trouble. I am also thankful to Aditya Nigam, Ashish Agrawal, Kamalesh Tiwary, Sumit Kalra for their important suggestions that paved the way for my success.

I express my gratitude towards my parents, my elder sister and a dear friend for their love, constant support and encouragement. I am indebted to all my school friends, college friends for making these days memorable and interesting. I am fortunate enough to have friends like Subhashish, Souvik, Neetesh, Debayan, Mayukh, Jay, Akhil, Manash, Modi, Hudda, Atanu, Chiradeep, Jaydeep, Jayesh, Arijit, Sumanta with whom I shared many memorable moments. I feel proud to be a part of M.Tech Batch 2011-13, where geniuses, future leaders, entrepreneurs cultivated their talents. Unity being the main \emph{mantra} of our batch, we believe to stay connected forever.

Last but not the least, I would like to thank faculty and staff of Computer Science and Engineering for creating such an wonderful academic environment. Lastly, I must say Indian Institute of Technology Kanpur, is the best place in India to nurture your talent.
\vskip 4mm
\begin{flushright}
\textit{\textbf{Debjyoti Paul}}
\end{flushright}




